How does increasing $s$ and $k$ effect log normalising constant estimation

### 2023-04-11 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Run k = 3 and s = 1:5 experiments, then put into comparison report (plus generalise that a little to deal with more quadratures) #22

We start by reading in a selection of fitted PCA-AGHQ models:

```{r}
s1k2 <- readRDS("depends/aghq-s1-k2.rds")
s2k2 <- readRDS("depends/aghq-s2-k2.rds")
s3k2 <- readRDS("depends/aghq-s3-k2.rds")
s4k2 <- readRDS("depends/aghq-s4-k2.rds")
s5k2 <- readRDS("depends/aghq-s5-k2.rds")
```
# Table processing

```{r}
lognormconsts <- c(
  s1k2$quad$normalized_posterior$lognormconst,
  s2k2$quad$normalized_posterior$lognormconst,
  s3k2$quad$normalized_posterior$lognormconst,
  s4k2$quad$normalized_posterior$lognormconst,
  s5k2$quad$normalized_posterior$lognormconst
)

>>>>

We start by reading in a selection of fitted PCA-AGHQ models.
We only need the quadrature part of the returned object:

```{r}
read_sk <- function(s, k) {
  assign(paste0("s", s, "k", k), readRDS(paste0("depends/aghq-s", s, "-k", k, ".rds"))$quad, envir = parent.frame())
}

read_sk(s = 1, k = 2)
read_sk(s = 2, k = 2)
read_sk(s = 3, k = 2)
read_sk(s = 4, k = 2)
read_sk(s = 5, k = 2)

read_sk(s = 1, k = 3)
read_sk(s = 2, k = 3)
read_sk(s = 3, k = 3)
read_sk(s = 4, k = 3)
read_sk(s = 5, k = 3)
```

Check that a few of the runs have the correct number of grid points:

```{r}
stopifnot(nrow(s5k2$modesandhessians) == 2^5)
stopifnot(nrow(s3k3$modesandhessians) == 3^3)
```

# Table processing

```{r}
lognormconsts <- c(
  s1k2$normalized_posterior$lognormconst,
  s2k2$normalized_posterior$lognormconst,
  s3k2$normalized_posterior$lognormconst,
  s4k2$normalized_posterior$lognormconst,
  s5k2$normalized_posterior$lognormconst
)
